---
title: "R Cheat Sheet"
author: Paulo Monteiro
output:
  pdf_document:
    number_sections: yes
---

This is an R Markdown cheat sheet.

# Getting Started
## Basics

 **Assigning a value to an object/variable** (*R is case sensitive*):
```{r}
x = 16
x
str <- "a string"
str
```

**Lists all objects created in the workspace memory**:
```{r}
ls()
objects()
```

**Remove object from workspace memory**:
```{r}
rm(str)
ls()
```

**Inspect a command**:
```{r}
?sqrt
```

## Vectors, Lists and Matrices

**Creating a vector of integers and strings**:
```{r}
x=c(1,2,3,4,5);
x
colours=c("blue", "red")
colours
```

**Creating a sequence of elements**:
```{r}
2:9; 
seq(from=2, to=10, by=2)
```

**Repeat a number '1' or string 'hello' 5 times**:
```{r}
rep(1,times=5);rep("hello",times=5)
```

    
    
    x=1:5; y=x+10
    Creating a list and adding 10 to each element (*, /, - and + apply)
    
    
    x=1:5; y=5:1; x+y
    if two vectors are of the same length we may add/subtract/mult/div its elements
    
    
    x=1:5; x[1]=16
    Assigning 16 to index '1' of vector x
    
    
    y[c(1,3)]
    Select the first two elements of vector y
    
    
    y[-c(1,3)]
    Select all elements of vector y apart from the two first elements
    
    
    y[y<3]
    Select all elements less than 3 from vector y
    
    
    mat=matrix(c(1,2,3,4,5,6,7,8,9), nrow=3, byrow=TRUE)
    Create a matrix 3x3 with values entered by row
    
    
    mat[1,2]
    Extract an element from the matrix
    
    
    mat[c(1,3),2]
    Return elements 1 and 3 from column 2
    
     mat[,1]
    Return all elements from column 1
    
    
    mat[2,]
    Return all elements from the second row

Add another line to resume regular para